\documentclass{scrartcl}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}

%% Sets page size and margins
\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

%% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

%% bibliography
\usepackage[square,numbers]{natbib}
\bibliographystyle{abbrvnat}
\title{Discrete event simulation of different selfish mining strategies in Bitcoin}
\subtitle{Master Thesis Proposal}
\author{Advisor: Edgar Weippl}

\begin{document}
\maketitle

\section{Problem statement}
The cryptocurrency Bitcoin started back in the year 2008 with the release of the Bitcoin white paper \cite{nakamoto2008bitcoin} and reached as of today a market capitalization of over 20 billion dollars \cite{MarketCap2017, Coindesk2017}. Internally the Bitcoin cryptocurrency records all transactions in a public ledger called the blockchain. The blockchain is basically an immutable linked list of blocks where a block contains multiple transactions of the cryptocurrency. In Bitcoin, each block needs to contain a so-called proof of work (PoW) which is the solution to a costly and time-consuming cryptographic puzzle. Miners connected in a peer-to-peer network compete with their computation power to find solutions to the puzzle and hence to find the next block for the blockchain. Finding a block allows the miners to add a transaction to the block and gives them a certain amount of bitcoins out of thin air. Additionally, the grouping of the transaction in blocks creates an ordering for the transaction and makes it possible to prevent double-spending. After a block is found by a miner all other miners should adopt to this new tip of the chain and try to find a new block on top. This mining process is considered as incentive compatible as long as no single miner has more than 50\% of the total computation power.

\citeauthor{eyal2014majority} showed that also miners under 50\% have an incentive to not follow the protocol as described depending on their connectivity in the peer-to-peer network and computation power. By implementing a so-called selfish mining strategy a miner can obtain relatively more revenue than his actual proportion of computational power in the network. In general, the miner simply does not shares found blocks with the others and secretly mines on his own chain. At some point, the public miners will catch up with their public chain because they have over 50\% of the computation power. In this case, the selfish miner publishes his blocks. If his chain is longer then the public chain, he is able to overwrite all blocks found by the honest miners. If the two chains have the same length the private miner also publishes his block and causes a block race. Now the network is split into two parts where one part is mining on the public tip and the other part is mining on the now public-private tip. In general, the selfish miner achieves that the other miners are wasting their computational power on blocks which will not end up in the longest chain.

%Nevertheless, in the short run, the selfish mining is not always profitable. Because of the waste of computational power caused by selfish mining fewer blocks are found. The selfish miner can increase his relative share but since there are fewer blocks often the honest behaviour would be more profitable. The selfish miner has to wait until the difficulty of the PoW-puzzle is adjusted to the now lower computational power of the network which happens in Bitcoin every two weeks. \cite{gervais2016security}

Further research \cite{nayak2016stubborn,sapirshtein2016optimal, gervais2015tampering, gervais2016security, bahack2013theoretical} explored different modifications of the original selfish mining algorithm by \citeauthor{eyal2014majority} and found slightly modifications of the algorithm which perform better under certain circumstances. For example, it could make sense for the selfish miner to even trail behind the public chain.

To prove the existence and attributes of selfish mining different approaches were applied. The researchers used simple probabilistic arguments \cite{eyal2014majority, bahack2013theoretical}, numeric simulation of paths with state machines \cite{gervais2015tampering, nayak2016stubborn}, advanced Markov Decision Processes (MDP) \cite{sapirshtein2016optimal, gervais2016security} or gave results of closed-source simulations \cite{eyal2014majority, sapirshtein2016optimal}. Unfortunately, we cannot discuss the closed source simulations but all other methodologies do not use discrete event simulation (DES) \cite{fishman1978principles} to simulate selfish mining. This type of simulation would allow reducing the abstraction used in the above-mentioned methodologies. One of the main abstraction introduced by the other researchers is that they model the block races with a simple probabilistic distribution. With a DES-simulation, it would be possible to model the whole network topology and simulate selfish mining under more realistic conditions. Hence the simulation could capture network delays and natural forks of the chain.




\section{Expected result}
The expected outcome of this thesis is a DES simulation of different selfish mining strategies. The selfish mining strategies used in the simulation are:
\begin{itemize}
\item selfish mining \cite{eyal2014majority}
\item lead stubborn mining \cite{nayak2016stubborn}
\item trail stubborn mining \cite{nayak2016stubborn}
\item equal-fork stubborn mining \cite{nayak2016stubborn}
\end{itemize}

For the simulation these strategies are combined with different distributions of computation power between the nodes and different network topologies. The result of the simulations should show which strategy is the best strategy for a certain combination of a network topology and distribution of computation power. 

Furthermore, the simulations should emphasise the recent work in the area of selfish mining and show that the current implementation of Bitcoin protocol is vulnerable against different selfish mining strategies.

\section{Methodology and approach}
First, the different mining strategies selfish, lead stubborn, trail stubborn and equal-fork stubborn mining from \citeauthor{nayak2016stubborn} and \citeauthor{eyal2014majority} need to be implemented. This is achieved by implementing a proxy which eclipses a normal Bitcoin client from the other nodes in the network. Now, if a block is found the proxy decides, depending on his selfish mining strategy, if a block should be transmitted from the eclipsed node to the rest of the network or vice versa. The design pattern proxy makes it possible to implement the selfish mining strategies without altering the reference implementation of Bitcoin and is therefore preferred over an implementation directly in the Bitcoin client.

In the next step, a DES simulation program is implemented. To be able to control when a certain node finds a block all Bitcoin nodes are executed in test mode. In test mode the real proof of work algorithm is disabled and every node accepts a command which lets the node create immediately a new block. With this functionality, it is possible to define a block discovery series which basically reflects the computation power of each node. The more blocks are found by a node the more simulated computation power the node has. Additionally to the block generation, the simulation program should also control the network topology and hence the connectivity of each node. For the simulation run, it is important that the connectivity of the nodes stays the same to make the results better comparable. This should be achieved by setting the connections from the nodes by the simulation program itself which is in contrast to normal behaviour. Normally Bitcoin nodes share their connections with other nodes over the Bitcoin protocol and try to improve the connectivity over time.

After the implementation of the selfish mining strategies and the DES simulation program, the mining strategies are simulated. Different settings for the connectivity and distribution of computation power are used to compare the profitability of the selfish mining strategies to the normal, honest mining.
\section{State-of-the-art}
bitcoin
selfish mining
each paper
countermeasures
no countermeasures implemented

\section{Relation to "Software Engineering and Internet Computing" curriculum}
Bitcoin, the overlying topic, is a relatively new technology. Hence there are no concrete subjects or modules teaching this technology in the current curriculum. But under the hood Bitcoin technically is just a composition of different technologies which can be related to modules of the curriculum. First of all, Bitcoin is a software acting as a distributed system and can, therefore, be linked to the modules \textit{Software Engineering} and \textit{Distributed Systems}. Furthermore, Bitcoin uses cryptography to secure the system, which can be linked to the module \textit{Advanced Security}. Hash functions are the main component of the proof of work algorithm in the mining process which solves the double spending problem in a novel way. To secure the bitcoins held by the different users of the system digital signatures based on cryptography are used.

In the thesis, the implementation of a proxy enabling selfish mining strategies and a DES simulation program are carried out. Since both of them are an implementation effort they can be directly linked to the module \textit{Software Engineering}. Furthermore, both software programs are related directly to the module \textit{Distributed Systems}. The proxy needs to be suited between multiple public nodes and one private in a Bitcoin network which is a distributed system and the simulation program needs to start-up, manage and tear-down this distributed system.

\bibliography{sample}

\end{document}