what are we doing now?
 - describing proxy \todo{okay to write what I am doing now?}
 - central point which implements selfish mining
 - relays and withholds blocks
 - not relaying tx

why we used a proxy?
 - fast implementation
 - no need to touch reference implementation

disadvanteges
 - extra hop
 - not a real proxy
   - need to keep track of chain
   - bitcoin protocol not easy

create a component diagram
 - network
 - chain
 - strategy
create a picture showing how blocks are relayed in bitcoin
\todo{any software recommendation for charts/diagrams}
 
\section{Communication}
 - how did we implement it?
   - based on pycoin of decker and python-bitcoinlib of todd
   - using gevent and hence co-routines to handle request
   - listening for incoming connections
   - private ip recognized because of unique ip
 - block relay
   - how does block relay work
   - compact blocks
   - how did we implement it
     - no compact blocks
     - assuming all blocks are valid
     - when we have the whole block pass it to chain

\section{Chain}
 - how did we implement it?
   - data structure
   - private/public highest tip
   - transfer\_allowed
   - block arrives, try to insert in chain. yes or orphaned. if yes check if orphaned can be added.
   - check if fork changed? pass it to strategy

\section{Strategy}
 - receives height of private and public
 - searches action to execute
   - 4 different types of actions (wait, adopt, match, implement)
 - executes by sending inv's
 - which strategies did we implement?
 - \todo{how works each strategy? describe it here or in section simulation and reference to the section.}
 - how did we implement it?
   - search for an action
   - if-else control structure
   - many unit tests
   
